Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-28 paper/main.tex
Ack comments

\todo[inline]{I think you need to help the reader understand, what annotations
in the AV-movie are relevant in the current context; COH: revised the section a
little. Most importantly the "cinematographic rationale" is explained first and
is then followed by the categories; imo annotations are more important in
section "contrasts"}

@@

\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
these? COH: no clue what to do with that feedback}
% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
Maximum correlations are found for low-level auditory confounds across
stimuli,
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
between root mean square volume of both audio tracks, r=.76; correlation between
left-right volume difference of both audio tracks, r=.77).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; Tab.~\ref{tab:events} for a
        description) and audio-visual movie (red; Tab.~\ref{tab:events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}

>>>>

@@

% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
Maximum correlations are found for low-level auditory confounds across
stimuli,
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
between root mean square volume of both audio tracks, r=.76; correlation between
left-right volume difference of both audio tracks, r=.77).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of model response time series used as regressors in
        the GLM analysis of the
        audio-description (blue; Tab.~\ref{tab:events} for a
        description) and audio-visual movie (red; Tab.~\ref{tab:events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}
